---
title: "GLM Poisson Regression Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GLM Poisson Regression Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Poisson Regression Example 

 In this vignette we'll build a simple model from r`glm`'s help function and
 deploy it to Verta.

# Building the model
```{r poisson regression}
## Dobson (1990) Page 93: Randomized Controlled Trial :
counts <- c(18,17,15,20,10,20,25,13,12)
outcome <- gl(3,1,9)
treatment <- gl(3,3)
original_df <- data.frame(treatment, outcome, counts) # showing data
original_df
```


```{r fit poisson regression}
glm.D93 <- glm(counts ~ outcome + treatment, family = poisson())

```

Test predictions with a simple datapoint.
```{r test }
predict(glm.D93,newdata = data.frame(outcome ="1",treatment  = "2" ))
```

## Prepare the Prediciton object for Deployment

 In this case we simply pass the object. The other parameters are not actually needed.
 The structure of the object is as follows:
 * model_file - the object we call the r`predict` function on.
 * formula_obj - optional, 
 
```{r}
poisson_model_object <- list(
  model_file = glm.D93
)

saveRDS(poisson_model_object,"poisson_model_object.RData")
```

## Set up Verta Connection


```{r}
library(stringr)
reg_random_string <- rpois(1,1000)
experiment_random_string <- rpois(1,1000)

reg_random_string <- rpois(1,1000)
experiment_random_string <- rpois(1,1000)

PROJECT_NAME <-  str_glue("Poisson GLM Example {reg_random_string}")
EXPERIMENT_NAME <-  str_glue("Poisson GLM Example {experiment_random_string}")
WORKSPACE <-  "Stefan_Petrov"

# library(vertaReticulateClient)
HOST = "dev.verta.ai"


Sys.setenv(VERTA_EMAIL= "...",
          VERTA_DEV_KEY = "...")
assertthat::see_if(
  (length(Sys.getenv("VERTA_EMAIL"))>1)&(
    length(Sys.getenv("VERTA_DEV_KEY"))>1
  )
)
library(vertaReticulateClient)
init_verta(HOST)
proj <- set_project(name=PROJECT_NAME)
experiment <- set_experiment(name=EXPERIMENT_NAME)
```



```{r}
run <- set_experiment_run(name=EXPERIMENT_NAME,desc = "Poisson Model Run")
# run$log_model(model = "poisson_model_object.RData",overwrite = T)# # TODO- add# run_log
log_model(run, "poisson_model_object.RData", overwrite = T)

```
## Download the model
```{r}
run$download_model("./poisson_model_object_downloaded.RData")

downloaded_model <- readRDS("poisson_model_object_downloaded.RData")# this
downloaded_model 
```
## Build the Docker image
```{r}
# createDockerContextZip(
#   "poisson_model_object_downloaded.RData",
#   required_packages = c() 
#   )
```

```{r,eval=FALSE,echo=FALSE}
buildDocker(location = "docker_folder_WZRUV5146S/",tag="verta-poisson:latest")
```


run it
```{bash,eval=F}
docker kill $(docker container ls -q)
docker run -p 8000:8000 verta-poisson:latest
```

Example http call and response:
### Post to verta-poisson

POST http://localhost:8000/score
Content-Type: application/json

[{"treatment":"1","outcome": "1"}]


### Response


HTTP/1.1 200 OK
Date: Fri, 30 Jul 2021 17:03:38 GMT
Content-Type: application/json
Content-Length: 8

[
  3.0445
]

Response code: 200 (OK); Time: 143ms; Content length: 8 bytes



