---
title: "Verta Forecasting and Custom Predict Functions"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

# Setup and libraries to load

```{r}
library(data.table)
library(magrittr)
library(stringr)
library(yardstick)
# library(hts)
library(ggplot2)
library(forecast)
library(ggplot2)
library(forecast)
library(stringr)

```


# Setup

```{r}
reg_random_string <- rpois(1,1000)
experiment_random_string <- rpois(1,1000)

reg_random_string <- rpois(1,1000)
experiment_random_string <- rpois(1,1000)

PROJECT_NAME <-  str_glue("Forecasting Examples {reg_random_string}")
EXPERIMENT_NAME <-  str_glue("Forecasting Example {experiment_random_string}")
WORKSPACE <-  "Stefan_Petrov"

# library(vertaReticulateClient)
HOST = "dev.verta.ai"
Sys.setenv(VERTA_EMAIL= "...",
          VERTA_DEV_KEY = "...")

library(vertaReticulateClient)
```
```{r}
# install_verta(method="system")
```

## Python verstions

 ### System python coase
 
```{r}

# library(reticulate)
# reticulate::use_python("/usr/bin/python3",required=T)# install verta from python console by
# using pip install verta
```
 


```{r}
## then if using system python, pass the path as well.
# point to the python path one can use
# init_verta(HOST,method = "auto",python_path = "/usr/bin/python3")

init_verta(HOST)
```

## Initialize Client, experiments, etc

```{r}
proj <- set_verta_project(name=PROJECT_NAME)
experiment <- set_verta_experiment(name=EXPERIMENT_NAME)
```

## Auto Arima Example

We'll use the WWWusage dataset by Durbin and Koopman, containing the
number of users.

```{r create_arima_model}
run <- set_experiment_run(name=EXPERIMENT_NAME,desc = "Forecasting Experiment 2")
# train-test
WWWusageTrain <- WWWusage[1:floor(length(WWWusage)/2+0.01)]
WWWusageTest <- WWWusage[(length(WWWusageTrain)+1):length(WWWusage)]
# we'll create an auto-arima model
WWWusageFit <- auto.arima(WWWusageTrain)
```

```{r log_params}
log_run_hyperparameters(run,hyperparams = list(dataset_name ="WWWusage",
                                               seasonality = NULL,
                                               trainSetLength = length(WWWusageTrain)
                                               ),overwrite = T)

# accuracy(WWWusageFit)
# run_log_metric(run,key = "rsquared",value = rsq)
autoplot(forecast(WWWusageFit,h=20))
```

## Custom Perdict Method

The verta deployment object requires the model object to have a
`predict` method attached. The `forecast` method is not completely
appropriate if we would like like to give them model a new chunk of data
and predict the next period without re-fitting.

To that end, we use a 2-step process:

1.  Create a light wrapper around your model object, give it a unique
    class name to prevent accidental method overload issues.

```{r}
WWWusageFit <- list(model=WWWusageFit)
class(WWWusageFit) <- "newForecaster"

```

2.  Use the process, outlined in [this blog
    post](library(forecast)%20fit%20%3C-%20ets(trainingdata)%20fit2%20%3C-%20ets(testdata,%20model=fit)%20onestep%20%3C-%20fitted(fit2)),
    in order to create out-of-sample predictions.

```{r}
# setup a predict.Arima object
# this will return the expectation for the first period after. Adjust as needed to predict multiple steps.
# by convention, the deployed verta prediction endpoints return a single value, but you can return multiple values, the full data frame with the quantiles required, etc
# the predict method assumes we get a data frame, so 
# the data we send to this method will be a dataframe,
# ordered by date, with the 'value' column as value

predict.newForecaster <- function(mdl,newdata,colname="value"){
  
  if(is(newdata,"data.frame")){
    newdata= newdata[[colname]]
  }
  
  modI <- mdl[["model"]]
  # print(class(modI))
  # print(modI)
  mod <- Arima(y=newdata,model = modI)
  fct_obj <- forecast(mod)
  # print("class of forecasting object")
  # print(class(fct_obj))
  as.data.frame(fct_obj)[1,1] 
}
```

We can call the predict method with some random data to verify:

```{r}
ll <- predict(WWWusageFit,newdata=data.frame(value=rnorm(10)))
ll
```

### Additional Steps

Additional functions we would like to wrap, besides the model object,
should be kept in a separate file.

NB- later fold this into whatever we upload

```{r}
save(list=c("predict.newForecaster"),file = "additional_objects.RData")
```

```{r}
save_model_data(file_to_save_at = "fctArtifact.RData",
                  modFile = WWWusageFit,
                  # formula_obj = "mpg~.",
                  # original_df = WWWusageTrain,
                  required_packages = c("forecast"),
                  additional_objects = list("predict.newForecaster"=predict.newForecaster)
                  )
```

```{r}
# fct
```



```{r}

# first_model_object <- list(
#   model_file = WWWusageFit,
#   formula_obj = "mpg~.",
#   original_df = WWWusageTrain,
#   required_packages=c("forecast"),
#   additional_objects=list(
#     "predict.newForecaster"=predict.newForecaster
#   ),
#   
#   
# )
# 
# saveRDS(first_model_object,"WWWUsage_object.RData")

```

### Log the model for future usage

```{r}
run$log_model(model = "fctArtifact.RData",overwrite = T)# # TODO- add# run_log
```

```{r}
run$download_model("./usage_object.RData")
# run$download_model("./dl_model/")

downloaded_model <- readRDS("usage_object.RData")# this
downloaded_model # this is what it should be

```

### Create Docker Context

```{r}
createDockerContextZip(
  "usage_object.RData"
  # required_packages = "forecast"
  #,
  #additional_objects_file_location="additional_objects.RData"
)
```

### The above docker context could be build

```{r}
buildDocker(location = "docker_folder_FCWAG0602T/",tag = "verta-forecast:latest")
```

Test with

    POST http://localhost:8000/score
    Content-Type: application/json

    [{"value":1},{"value":2},{"value":3},{"value":4},{"value":5},{"value":6},{"value":7},{"value":8}]
