---
title: "Verta Reticulate Workflow"
output: html_notebook
---

This is closely following this [jupyter notebook](https://github.com/VertaAI/modeldb/blob/master/client/workflows/demos/dataset-registry-endpoint.ipynb)

# Setup

```{r}
library(reticulate)
library(data.table)
library(magrittr)
library(stringr)
library(yardstick)
# use_condaenv("verta_reticulate",required=T)
# library(vertaReticulateClient)
```

```{r}
reg_random_string <- rpois(1,1000)

HOST = "dev.verta.ai"
PROJECT_NAME <-  str_glue("MTCARS Regression{reg_random_string}")
EXPERIMENT_NAME <-  "Linear Regressions"
WORKSPACE <-  "Stefan_Petrov"
Sys.setenv(VERTA_EMAIL= "...",
           VERTA_DEV_KEY = "...")
```

## Initialize Client

```{r}
library(vertaReticulateClient)
vertaReticulateClient::init_verta(HOST)
# cl <- get_verta_client()
# cl$create_dataset()
proj <- vertaReticulateClient::set_verta_project(name="Reticulate MTCars")
experiment <- vertaReticulateClient::set_verta_experiment(name="Verta R Experiment")
```

## Use mtcars for the experiment

```{r train_test_split}
N <- nrow(mtcars)
trainSet <- mtcars[1:floor(N/2),]
testSet <- mtcars[(floor(N/2)+1):N,]
```

## Create 2 registered models to compate

```{r create_lm_model}
run <- set_experiment_run(name="MTCars Experiment 4",desc = "MtCars Experiment 4")
log_run_hyperparameters(run,hyperparams = list(hyperparam1=1,hyperparam2=2),overwrite = T)
log_run_hyperparameters(run,hyperparams = list(formula="mpg~."),overwrite = T)

mod_mtcars <- lm(mpg~.,data = trainSet)

summary_lm <- summary(mod_mtcars)
rsq <- summary_lm$adj.r.squared
# run_log_metric(run,key = "rsquared",value = rsq)

```

```{r create_lm_model_2}
run2 <- set_experiment_run(name="MTCars Experiment 3",
                           desc = "MTCars Experiment 3")
log_run_hyperparameters(run2,hyperparams = list( formula=
                                                 "mpg~cyl+disp+hp+drat+wt+qsec+vs"
                                               ),overwrite = T)
mod_mtcars_2 <- lm(mpg~cyl+disp+hp+drat+wt+qsec+vs,data = trainSet)
summary_lm_2 <- summary(mod_mtcars_2)
rsq_2 <- summary_lm$adj.r.squared
run_log_metric(run2,key = "rsquared",value = rsq_2,overwrite = T)

```

So we created some 2 experiment runs and added some metrics for them...

## Log Model and Upload Artifacts

```{r}
first_model_object <- list(
  model_file = mod_mtcars,
  formula_obj = "mpg~.",
  original_df = trainSet,
  required_packages="",
  additionalObjects=list()
)

saveRDS(first_model_object,"mpg_experiment_object.RData")
run$log_model(model = "mpg_experiment_object.RData",overwrite = T)# TODO- add
# run_log
```

The downloaded model is almost what's needed. From the web UI it works fine.

```{r download_model_buggy}
# there is some issue with this
# run$download_model("downloaded_model.RData")
run$log_model(model = "mpg_experiment_object.RData",overwrite = T)# TODO- add
run$download_model("./dl_model/download_model.RData")
# run$download_model("./dl_model/")

downloaded_model <- readRDS("./dl_model/download_model.RData")# this
downloaded_model # this is almost what it should be, but not quite...
downloaded_model_lm <- downloaded_model[["model_file"]]
downloaded_model_lm

```

### We'll use downloaded_model to build a docker service

```{r}
lm_model_from_download <- downloaded_model$model_file
```

## Find the best run and it's hyperparameters

```{r}
best_run <- get_best_run_by_metric(experiment,
                                   "metrics.rsquared",descending = T)
best_run_hyperparameters <- best_run$get_hyperparameters()
```

# Register the Best Model as in the jupyter

```{r}

registered_model_best_mtcars <- get_or_create_registered_model(name="mtcars_best",
                                                               workspace = WORKSPACE)
registered_model_best_mtcars$create_version_from_run(best_run$id,name="v5")
```

## Model Deployment

Here we simply use the downloaded_model in order to deploy a service at localhost:8000

```{r model deployment}

runner_template_location <- file.path(path.package("vertaReticulateClient"),
"to_run.R"
)

plumber_template_location <- file.path(path.package("vertaReticulateClient"),
                                         "plumber_sample.R"
)


createDockerfile(
  model_file_location = "../mpg_model.RData",
  # model_file_location = downloaded_model, 
  runner_template_location = runner_template_location,
  plumber_template_location = plumber_template_location,
  required_packages = "forecast"
  )

# library(stringr)

# runDocker(location =".",
#           tag = "verta-plumber"
# )



```

now test w/ the following reques request:

curl -X POST --location "<http://localhost:8000/score>"\
-H "Accept: application/json"\
-d "{"cyl":8,"disp":440,"hp":230,"drat":3.83,"wt":5.345,"qsec":17.42,"vs":0,"am":0,"gear":3,"carb":4,"\_row":"Chrysler Imperial"}"

------------------------------------------------------------------------

Or

POST <http://localhost:8000/score> Accept: application/json

{"cyl":8,"disp":440,"hp":230,"drat":3.83,"wt":5.345,"qsec":17.42,"vs":0,"am":0,"gear":3,"carb":4,"\_row":"Chrysler Imperial"}
```{r}
createDockerfileWithFolder(
  model_file_location = "../mpg_model.RData",
  # model_file_location = downloaded_model, 
  runner_template_location = runner_template_location,
  plumber_template_location = plumber_template_location,
  required_packages = "forecast"
  )

inst
```

